%%% Author: mterenui (F.M.T. C)
%%% Docs: https://github.com/xxx
%%% License: GNU General Public License v3.0
%%% This document is provided as a general template for informational purposes only and does not constitute legal advice. Permission is granted to copy, modify, and use this template for personal or commercial purposes, provided that this copyright and license notice is retained in all copies or substantial portions of the document. The author makes no representations or warranties regarding the legal validity or enforceability of this template in any jurisdiction. Users are strongly encouraged to consult a qualified legal professional before using this document.

\section{Maintenance and Repair}
\label{sec:maintenance}

\subsection{Landlord Responsibilities}
\label{sec:landlordresponsibilities}
The Landlord shall be responsible for maintaining the structural integrity of the Premises, including the roof, walls, foundation, and exterior, as well as ensuring that the plumbing, electrical, heating, and cooling systems are in good working condition. The Landlord shall promptly address and repair any defects or malfunctions in these systems upon receiving written notice from the Tenant.

\subsection{Tenant Responsibilities}
\label{sec:tenantresponsibilities}
The Tenant shall keep the Premises clean and in good condition and shall promptly notify the Landlord in writing of any damage, defect, or necessary repair. The Tenant shall be responsible for repairing any damage caused by the Tenant’s negligence, misuse, or that of the Tenant’s family, guests, or invitees. Routine minor maintenance, such as changing light bulbs, fuses, or air filters, shall be the responsibility of the Tenant.

\subsection{Prohibited Alterations}
\label{sec:prohibitedalterations}
The Tenant shall not make structural changes, alterations, or additions to the Premises without the prior written consent of the Landlord. Any approved alterations shall become the property of the Landlord unless otherwise agreed in writing.

\subsection{Emergency Repairs}
\label{sec:emergencyrepairs}
In the event of an emergency repair necessary to prevent damage to the Premises or risk to health and safety, the Tenant may take immediate action to mitigate damage and shall notify the Landlord as soon as reasonably possible.

\subsection{Access for Repairs}
\label{sec:accessforrepairs}
The Landlord or their authorized agents shall have the right to access the Premises at reasonable times, upon prior notice, to inspect, maintain, or repair the Premises. In emergencies, access may be immediate without prior notice.

%%% End of document (maintenance.tex)