%%% Author: mterenui (F.M.T. C)
%%% Docs: https://github.com/xxx
%%% License: GNU General Public License v3.0
%%% This document is provided as a general template for informational purposes only and does not constitute legal advice. Permission is granted to copy, modify, and use this template for personal or commercial purposes, provided that this copyright and license notice is retained in all copies or substantial portions of the document. The author makes no representations or warranties regarding the legal validity or enforceability of this template in any jurisdiction. Users are strongly encouraged to consult a qualified legal professional before using this document.

\section{Exit and Termination}
\label{sec:exit}

\subsection{Termination by Tenant}
\label{sec:tenanttermination}
The Tenant may terminate this Agreement by providing the Landlord with \NoticePeriod{} days’ written notice prior to the intended move-out date. The Tenant shall vacate the Premises on or before the termination date and return all keys and access devices to the Landlord.

\subsection{Termination by Landlord}
\label{sec:landlordtermination}
The Landlord may terminate this Agreement by providing the Tenant with written notice in accordance with applicable law for reasons including, but not limited to, non-payment of rent, violation of lease terms, or damage to the Premises.

\subsection{Mutual Termination}
\label{sec:mutualtermination}
This Agreement may be terminated at any time by mutual written consent of both parties.

\subsection{Condition of Premises Upon Exit}
\label{sec:exitpremisecondition}
Upon termination, the Tenant shall:

\begin{itemize}
  \item Vacate the Premises and remove all personal belongings.
  \item Return the Premises in the same condition as received, reasonable wear and tear excepted.
  \item Return all keys, remotes, and access devices to the Landlord.
  \item Settle any outstanding rent, utilities, or other charges due under this Agreement.
\end{itemize}

%%% End of document (termination.tex)